### 2017-08-02 Paper01_EnthalpyAndCrystallization.tex
Results - DSC - wrote draft film DSC results

START HERE. Likely talking about Films!!!
Both the bulk and film \MgZnCa~ were examined at various \acrshort{dsc} heating rates (\acrshort{ht}) to observe changed in the \Tg~ and \Tx~ temperatures. As expected higher heating rates resulted in great signal strength, exothermic peaks shifting to higher temperatures, and increases in thermal lag resulting in curve convolution.

>>>>

The film was examined at \glspl{ht} of 15, 20, 30, 40, 60, 80, and 100 $K/min$. The lower \glspl{ht} of 5 and 10 $k/min$ were not utilised owing to the lower film signal compared to the bulk. The reduced signal was likely from the low mass of the film, about $\frac{1}{10}$ that of the bulk. The film showed the expected variable relationships with increasing \gls{ht} as observed in the bulk. The signal intensity increased at a compatible rate to bulk up until \glspl{ht} of 80 and 100 $k/min$. These final two \glspl{ht} showed great increases in the signal intensity. The exothermic peaks all convoluted together making many of thermodynamic events difficult to observer. The \Tg~ and \Tx $_{1}$s were less defined than for the bulk, but could still be identified for all \glspl{ht}. For all \glspl{ht} the \Tx $_{2-5}$ onsets could not be easily identified, see Figure \ref{fig:DSC_vHeatingRate_Film}.
